---
title: "World Bank Indicator Visualizations"
author: "Kyle Chen"
date: "2/21/2021"
output: rmarkdown::github_document
---
```{r setup, include=FALSE}
source("analysis.R")
library("knitr")
library("ggplot2")
```

## CO2 Emissions by Country
```{r CO2, echo=FALSE}
top_6_c02_plot
```

##### Insight:
All of the countries that are on this list are developed countries, except India.
According to the news from [the Washington Post](https://www.washingtonpost.com/climate-solutions/2020/06/12/india-emissions-climate/), "*Coal will remain a major part of India’s power sector in the coming decades, and the country is still building coal-fired plants.*" The government of India will need policies to lower pollution and carbon emissions in the near future, and from my perspective and the bar chart below, I believe they will need to find a more eco-friendly way to produce electricity, instead of relying on coal-fired plants.

## Sources of Electric Power in India 
```{r India Electricity, echo=FALSE}
india_electric_plot
```


<p>&nbsp;</p>
## Forestation over Time
One of the main contributors to global warming is deforestation. Based on the graph, countries that are closed to the equator are losing their forest throughout this time period.
```{r Forestation, echo=FALSE}
world_forest_plot
```

<p>&nbsp;</p>
## Population Trend in Japan From 1996 to 2020
```{r Japan population, echo=FALSE}
population_plot
```

##### Insight:
Japan starts to become an aging society in 1997, and clearly the gap between these two age groups is significantly increasing. According to the news from [Diplomat Media](https://thediplomat.com/2019/11/how-does-japans-aging-society-affect-its-economy/), "*Due to the nation’s aging and shrinking population, there is an increased need to address the labor shortage. People eventually retire and leave the workforce as they start aging, and at present, there are not enough young people in Japan to fill this vacuum owing to the decline in the fertility rate as well.*" One of the causes that might have effect to this factor is that Japan has a well-developed health care system and have kept developing, thus, their elder population keeps booming.